A Speculative Approach to Parallelization in Particle Swarm Optimization

### 2011-11-16 masters_thesis/si_paper/paper.tex
Final updates for the paper

We frequently present tables summarizing our results.  In each table, we bold
the ``best'' method, meaning that it has at least a 90\% success rate and its
average time to completion is faster than all other methods that have at least
a 90\% success rate\footnote{``Success rate'' here means that the algorithm
reached some predefined value which is mentioned in the table or figure
wherever a success rate is reported.}.  We used a double-sided t-test to test
for statistical significance in these results, and all algorithms whose values
are bolded are significantly superior to non-bolded algorithms with a p-value
of less than $10^{-5}$.

@@

\begin{table}
  \caption{Summary of results for function Sphere with 20 dimensions,
  measuring number of time steps to reach a value of 1e-35.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:sphere-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&0\%&N/A&N/A\\
  \hline
  Standard Random&0\%&N/A&N/A\\
  \hline
  Standard Complete&100\%&931.0&19.1\\
  \hline
  SEPSO Ring&0\%&N/A&N/A\\
  \hline
  SEPSO Random&85\%&972.8&15.8\\
  \hline
  Pick Best Ring&100\%&917.4&21.0\\
  \hline
  Pick Best Random&100\%&768.1&14.3\\
  \hline
  Pick Best Pruned Ring&100\%&967.8&9.9\\
  \hline
  Pick Best Pruned Random&100\%&693.5&10.4\\
  \hline
  \textbf{Pick Best Pruned Complete}&\textbf{100\%}&\textbf{389.6}&
    \textbf{9.6}\\
  \hline
  Social Promotion Pruned Ring&0\%&N/A&N/A\\
  \hline
  Social Promotion Pruned Random&100\%&971.1&10.6\\
  \hline
  Social Promotion Pruned Complete&100\%&777.8&16.7\\
  \hline
  Many Iterations Ring&100\%&575.2&9.8\\
  \hline
  Many Iterations Random&100\%&442.4&7.1\\
  \hline
  Many Iterations Complete&0\%&N/A&N/A\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Schwefel with 20 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:schwefel-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&0\%&N/A&N/A\\
  \hline
  Standard Random&0\%&N/A&N/A\\
  \hline
  Standard Complete&100\%&837.2&44.8\\
  \hline
  SEPSO Random&0\%&N/A&N/A\\
  \hline
  Pick Best Random&5\%&938.0&0.0\\
  \hline
  \textbf{Pick Best Pruned Random}&\textbf{100\%}&\textbf{639.9}&\textbf{29.4}\\
  \hline
  \textbf{Pick Best Pruned Complete}&\textbf{100\%}&\textbf{597.7}&
	\textbf{77.9}\\
  \hline
  Social Promotion Pruned Random&75\%&938.0&33.0\\
  \hline
  Social Promotion Pruned Complete&100\%&815.2&43.5\\
  \hline
  Many Iterations Random&100\%&783.5&94.5\\
  \hline
  Many Iterations Complete&0\%&N/A&N/A\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Rastrigin with 20 dimensions,
  measuring number of time steps to reach a value of 20.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:rastrigin-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&25\%&743.4&212.0\\
  \hline
  Standard Random&100\%&372.1&86.6\\
  \hline
  \textbf{Standard Complete}&\textbf{95\%}&\textbf{273.1}&\textbf{99.7}\\
  \hline
  SEPSO Ring&5\%&471.0&0.0\\
  \hline
  SEPSO Random&15\%&208.0&17.0\\
  \hline
  Pick Best Ring&35\%&489.0&152.0\\
  \hline
  Pick Best Random&15\%&136.0&40.1\\
  \hline
  Pick Best Pruned Ring&95\%&545.9&208.5\\
  \hline
  Pick Best Pruned Random&10\%&95.0&11.0\\
  \hline
  Pick Best Pruned Complete&5\%&59.0&0.0\\
  \hline
  Social Promotion Pruned Ring&5\%&580.0&0.0\\
  \hline
  Social Promotion Pruned Random&80\%&278.2&136.3\\
  \hline
  Social Promotion Pruned Complete&50\%&200.5&130.2\\
  \hline
  Many Iterations Ring&10\%&117.0&25.0\\
  \hline
  Many Iterations Random&5\%&57.0&0.0\\
  \hline
  Many Iterations Complete&0\%&N/A&N/A\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Griewank with 20 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:griewank-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&100\%&762.2&19.4\\
  \hline
  SEPSO Ring&100\%&426.0&81.0\\
  \hline
  \textbf{Pick Best Ring}&\textbf{100\%}&\textbf{272.0}&\textbf{17.7}\\
  \hline
  \textbf{Pick Best Pruned Ring}&\textbf{100\%}&\textbf{282.9}&\textbf{10.7}\\
  \hline
  Social Promotion Pruned Ring&100\%&482.0&16.6\\
  \hline
  Many Iterations Ring&84\%&183.2&49.4\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Bohachevsky with 20 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:bohachevsky-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Random&100\%&472.3&6.6\\
  \hline
  Standard Complete&100\%&238.2&11.2\\
  \hline
  SEPSO Random&75\%&261.6&9.2\\
  \hline
  Pick Best Random&100\%&211.8&9.2\\
  \hline
  Pick Best Pruned Random&100\%&189.7&3.4\\
  \hline
  Pick Best Pruned Complete&25\%&105.4&3.9\\
  \hline
  Social Promotion Pruned Random&100\%&260.3&6.5\\
  \hline
  Social Promotion Pruned Complete&90\%&197.9&12.2\\
  \hline
  \textbf{Many Iterations Random}&\textbf{94\%}&\textbf{118.2}&\textbf{2.6}\\
  \hline
  Many Iterations Complete&0\%&N/A&N/A\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Rastrigin with 50 dimensions,
  measuring number of time steps to reach a value of 100.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:rastrigin-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&5\%&776.0&0.0\\
  \hline
  \textbf{Standard Random}&\textbf{100\%}&\textbf{593.2}&\textbf{89.5}\\
  \hline
  Standard Complete&80\%&343.8&145.8\\
  \hline
  Many Iterations Ring&25\%&223.8&67.1\\
  \hline
  Many Iterations Random&25\%&98.6&11.0\\
  \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Summary of results for function Sphere with 50 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:sphere-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&0\%&N/A&N/A\\
  \hline
  Standard Random&30\%&986.8&8.2\\
  \hline
  Standard Complete&100\%&458.4&12.3\\
  \hline
  Many Iterations Ring&100\%&288.7&3.9\\
  \hline
  \textbf{Many Iterations Random}&\textbf{100\%}&\textbf{248.6}&\textbf{5.1}\\
  \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Summary of results for function Schwefel with 50 dimensions,
  measuring number of time steps to reach a value of 80.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:schwefel-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&0\%&N/A&N/A\\
  \hline
  Standard Random&70\%&871.6&57.1\\
  \hline
  Standard Complete&100\%&599.0&85.6\\
  \hline
  \textbf{Many Iterations Ring}&\textbf{100\%}&\textbf{238.6}&\textbf{34.2}\\
  \hline
  \textbf{Many Iterations Random}&\textbf{100\%}&\textbf{242.9}&\textbf{95.4}\\
  \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Summary of results for function Griewank with 50 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:griewank-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&100\%&1898.5&25.7\\
  \hline
  \textbf{Many Iterations Ring}&\textbf{97\%}&\textbf{312.4}&\textbf{6.3}\\
  \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Summary of results for function Bohachevsky with 50 dimensions,
  measuring number of time steps to reach a value of 0.01.  The ``best''
  algorithm is bolded, meaning that it has at least 90\% complete and its mean
  time to completion is significantly lower than all non-bolded algorithms,
  with a p-value of less than $10^{-5}$.}
  \label{tab:bohachevsky-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&100\%&1434.0&62.1\\
  \hline
  Standard Random&100\%&704.5&19.7\\
  \hline
  Standard Complete&20\%&377.5&14.9\\
  \hline
  \textbf{Many Iterations Ring}&\textbf{95\%}&\textbf{229.8}&\textbf{11.4}\\
  \hline
  Many Iterations Random&35\%&171.6&4.0\\
  \hline
  \end{tabular}
\end{table}

>>>>

We frequently present tables summarizing our results.  In each table, we bold
the ``best'' method, meaning that it has at least a 90\% success rate and its
average time to completion is faster than all other methods that have at least
a 90\% success rate\footnote{``Success rate'' here means that the algorithm
reached some predefined value which is mentioned in the table or figure
wherever a success rate is reported.}.  We used a double-sided t-test to test
for statistical significance in these results, and all algorithms shown in
boldface have a mean time to completion that is significantly lower than that
of other algorithms, with a p-value of less than $10^{-5}$.

@@

\begin{table}
  \caption{Summary of results for function Sphere with 20 dimensions,
  measuring number of time steps to reach a value of 1e-35.  The ``best''
  algorithm is shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 1e-35, and its mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:sphere-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&0\%&N/A&N/A\\
  \hline
  Standard Random&0\%&N/A&N/A\\
  \hline
  Standard Complete&100\%&931.0&19.1\\
  \hline
  SEPSO Ring&0\%&N/A&N/A\\
  \hline
  SEPSO Random&85\%&972.8&15.8\\
  \hline
  Pick Best Ring&100\%&917.4&21.0\\
  \hline
  Pick Best Random&100\%&768.1&14.3\\
  \hline
  Pick Best Pruned Ring&100\%&967.8&9.9\\
  \hline
  Pick Best Pruned Random&100\%&693.5&10.4\\
  \hline
  \textbf{Pick Best Pruned Complete}&\textbf{100\%}&\textbf{389.6}&
    \textbf{9.6}\\
  \hline
  Social Promotion Pruned Ring&0\%&N/A&N/A\\
  \hline
  Social Promotion Pruned Random&100\%&971.1&10.6\\
  \hline
  Social Promotion Pruned Complete&100\%&777.8&16.7\\
  \hline
  Many Iterations Ring&100\%&575.2&9.8\\
  \hline
  Many Iterations Random&100\%&442.4&7.1\\
  \hline
  Many Iterations Complete&0\%&N/A&N/A\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Schwefel with 20 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 1e-06, and its mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:schwefel-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&0\%&N/A&N/A\\
  \hline
  Standard Random&0\%&N/A&N/A\\
  \hline
  Standard Complete&100\%&837.2&44.8\\
  \hline
  SEPSO Random&0\%&N/A&N/A\\
  \hline
  Pick Best Random&5\%&938.0&0.0\\
  \hline
  \textbf{Pick Best Pruned Random}&\textbf{100\%}&\textbf{639.9}&\textbf{29.4}\\
  \hline
  \textbf{Pick Best Pruned Complete}&\textbf{100\%}&\textbf{597.7}&
	\textbf{77.9}\\
  \hline
  Social Promotion Pruned Random&75\%&938.0&33.0\\
  \hline
  Social Promotion Pruned Complete&100\%&815.2&43.5\\
  \hline
  Many Iterations Random&100\%&783.5&94.5\\
  \hline
  Many Iterations Complete&0\%&N/A&N/A\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Rastrigin with 20 dimensions,
  measuring number of time steps to reach a value of 20.  The ``best''
  algorithm is shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 20, and its mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:rastrigin-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&25\%&743.4&212.0\\
  \hline
  Standard Random&100\%&372.1&86.6\\
  \hline
  \textbf{Standard Complete}&\textbf{95\%}&\textbf{273.1}&\textbf{99.7}\\
  \hline
  SEPSO Ring&5\%&471.0&0.0\\
  \hline
  SEPSO Random&15\%&208.0&17.0\\
  \hline
  Pick Best Ring&35\%&489.0&152.0\\
  \hline
  Pick Best Random&15\%&136.0&40.1\\
  \hline
  Pick Best Pruned Ring&95\%&545.9&208.5\\
  \hline
  Pick Best Pruned Random&10\%&95.0&11.0\\
  \hline
  Pick Best Pruned Complete&5\%&59.0&0.0\\
  \hline
  Social Promotion Pruned Ring&5\%&580.0&0.0\\
  \hline
  Social Promotion Pruned Random&80\%&278.2&136.3\\
  \hline
  Social Promotion Pruned Complete&50\%&200.5&130.2\\
  \hline
  Many Iterations Ring&10\%&117.0&25.0\\
  \hline
  Many Iterations Random&5\%&57.0&0.0\\
  \hline
  Many Iterations Complete&0\%&N/A&N/A\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Griewank with 20 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithms are shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 1e-06, and their mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:griewank-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&100\%&762.2&19.4\\
  \hline
  SEPSO Ring&100\%&426.0&81.0\\
  \hline
  \textbf{Pick Best Ring}&\textbf{100\%}&\textbf{272.0}&\textbf{17.7}\\
  \hline
  \textbf{Pick Best Pruned Ring}&\textbf{100\%}&\textbf{282.9}&\textbf{10.7}\\
  \hline
  Social Promotion Pruned Ring&100\%&482.0&16.6\\
  \hline
  Many Iterations Ring&84\%&183.2&49.4\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Bohachevsky with 20 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 1e-06, and its mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:bohachevsky-20}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Random&100\%&472.3&6.6\\
  \hline
  Standard Complete&100\%&238.2&11.2\\
  \hline
  SEPSO Random&75\%&261.6&9.2\\
  \hline
  Pick Best Random&100\%&211.8&9.2\\
  \hline
  Pick Best Pruned Random&100\%&189.7&3.4\\
  \hline
  Pick Best Pruned Complete&25\%&105.4&3.9\\
  \hline
  Social Promotion Pruned Random&100\%&260.3&6.5\\
  \hline
  Social Promotion Pruned Complete&90\%&197.9&12.2\\
  \hline
  \textbf{Many Iterations Random}&\textbf{94\%}&\textbf{118.2}&\textbf{2.6}\\
  \hline
  Many Iterations Complete&0\%&N/A&N/A\\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Summary of results for function Rastrigin with 50 dimensions,
  measuring number of time steps to reach a value of 100.  The ``best''
  algorithm is shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 100, and its mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:rastrigin-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&5\%&776.0&0.0\\
  \hline
  \textbf{Standard Random}&\textbf{100\%}&\textbf{593.2}&\textbf{89.5}\\
  \hline
  Standard Complete&80\%&343.8&145.8\\
  \hline
  Many Iterations Ring&25\%&223.8&67.1\\
  \hline
  Many Iterations Random&25\%&98.6&11.0\\
  \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Summary of results for function Sphere with 50 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 1e-06, and its mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:sphere-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&0\%&N/A&N/A\\
  \hline
  Standard Random&30\%&986.8&8.2\\
  \hline
  Standard Complete&100\%&458.4&12.3\\
  \hline
  Many Iterations Ring&100\%&288.7&3.9\\
  \hline
  \textbf{Many Iterations Random}&\textbf{100\%}&\textbf{248.6}&\textbf{5.1}\\
  \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Summary of results for function Schwefel with 50 dimensions,
  measuring number of time steps to reach a value of 80.  The ``best''
  algorithms are shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 80, and their mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:schwefel-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&0\%&N/A&N/A\\
  \hline
  Standard Random&70\%&871.6&57.1\\
  \hline
  Standard Complete&100\%&599.0&85.6\\
  \hline
  \textbf{Many Iterations Ring}&\textbf{100\%}&\textbf{238.6}&\textbf{34.2}\\
  \hline
  \textbf{Many Iterations Random}&\textbf{100\%}&\textbf{242.9}&\textbf{95.4}\\
  \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Summary of results for function Griewank with 50 dimensions,
  measuring number of time steps to reach a value of 1e-06.  The ``best''
  algorithm is shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 1e-06, and its mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:griewank-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&100\%&1898.5&25.7\\
  \hline
  \textbf{Many Iterations Ring}&\textbf{97\%}&\textbf{312.4}&\textbf{6.3}\\
  \hline
  \end{tabular}
\end{table}

\begin{table}
  \caption{Summary of results for function Bohachevsky with 50 dimensions,
  measuring number of time steps to reach a value of 0.01.  The ``best''
  algorithm is shown in boldface.  This indicates that at least 90\% of runs
  successfully reach the value of 0.01, and its mean time to completion is
  significantly lower than all other algorithms, with a p-value of less than
  $10^{-5}$.}
  \label{tab:bohachevsky-50}
  \centering
  \begin{tabular}{|l|r|r|r|}
  \hline
  Algorithm&\% Complete&Mean&St. Dev.\\
  \hline
  \hline
  Standard Ring&100\%&1434.0&62.1\\
  \hline
  Standard Random&100\%&704.5&19.7\\
  \hline
  Standard Complete&20\%&377.5&14.9\\
  \hline
  \textbf{Many Iterations Ring}&\textbf{95\%}&\textbf{229.8}&\textbf{11.4}\\
  \hline
  Many Iterations Random&35\%&171.6&4.0\\
  \hline
  \end{tabular}
\end{table}
